\documentclass{article}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{indentfirst}
% \setlength{\parskip}{1em}
% \setlength{\parindent}{0.5in}

% Document
\begin{document}

\begin{titlepage}
	\centering
	\vspace*{\fill}

	\huge
	\textbf{Lab 4}

	\vspace{1cm}
	\Large

	% just putting us in alphabetical order for now
	\textbf{Sean Crowley}

	\textbf{Ethan Erdman}

	\textbf{David Templonuevo}

	\textbf{Cody Saunders}

	\vspace{0.5cm}
	ECE-571

	% Due Date
	\vspace{0.5cm}
	\today

	\vspace*{\fill}
\end{titlepage}

\section*{Introduction}

\noindent Our group chose to do project 6, the 8-bit asynchronous comparator:

\begin{enumerate}[start=6]
	\item 8-bit asynchronous comparator. The comparator operates asynchronously with an 8-bit input for comparison. It features an asynchronous global clear signal with active low. To maintain precision, the output is constrained to 16 bits to prevent overflow. The comparator requires a minimum input data rate of 1MHz. This ensures optimal performance, with a load capacitance of 1pF across all output pins. During a reset triggered by the global clear signal, all input signals are disregarded, ensuring a clean initialization state for the comparator.
\end{enumerate}

\noindent Some assumptions made about the project as well as clarifications asked about:

\begin{itemize}
	\item The prompt asking for a 16 bit output is a typo, and it will be 3 outputs instead, one for each of the possible comparisons (greater than, less than, equal to).
	\item The 8-bit inputs will not be signed, so we don't have to worry about two's (or one's) complement, nor will we have to worry about whether we're comparing magnitude or value.
\end{itemize}


\section*{Design Process}

\section*{Results}

\section*{Conclusion}

\end{document}